Light inextensible strings (threads) under tension in the Schwarzschild geometry: a new interpretation for ``straight line'' in general relativity

### 2020-10-21 string_physics_teacher_revision.tex
Physics Teacher house style

\begin{abstract}

Light inextensible string (thread) under tension is a stalwart feature
of elementary physics.  Here I show how considering such string in the
vicinity of a black hole, with the help of computer algebra systems,
can generate insight into the Schwarzschild geometry in the context of
an undergraduate homework problem, specifically by re-interpreting the
concept ``straight line''.  Light taut strings minimize their proper
length, given by integrating the spatial component of the
Schwarzschild metric along the string.  The path itself is given by
straightforward numerical solution to the Euler-Lagrange equations.
If the string is entirely outside the event horizon, its closest
approach to the singularity is tangential.  At this point the string
is {\em visibly} curved, surely a memorable and informative insight.
The geometry of the Schwarzschild metric induces some interesting
nonlocal phenomena: if the distance of closest approach is less than
about $1.0761\cdot 2M$, the string self-intersects, even though it is
everywhere under tension.  Light taut strings furnish a third
interpretation of the concept ``straight line'', the other two being
null geodesics and free-fall world lines.

% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}
\end{abstract}

@@

>>>>

% \PACS{PACS code1 \and PACS code2 \and more}
% \subclass{MSC code1 \and MSC code2 \and more}

@@

Light inextensible string (thread) under tension is a stalwart feature
of elementary physics.  Here I show how considering such string in the
vicinity of a black hole, with the help of computer algebra systems,
can generate insight into the Schwarzschild geometry in the context of
an undergraduate homework problem, specifically by re-interpreting the
concept ``straight line''.  Other definitions of ``straight'' might
include null geodesic paths and worldlines of objects in free fall;
light taut string furnishes a third distinct interpretation.  The path
itself is given by straightforward numerical solution to the
Euler-Lagrange equations.  At closest approach to the event horizon,
the string is tangential; at this point the string is {\em visibly}
curved, surely a memorable and informative insight.  The geometry of
the Schwarzschild metric induces some interesting nonlocal phenomena:
if the distance of closest approach is less than about $1.0761\cdot
2M$, the string self-intersects, even though it is everywhere under
tension.
